Supplementary material

### 2022-04-29 analysis/supplementary-materials/supplementary.Rmd
Minor edits

---
title: "Supplementary material"
author: "Isak Roalkvam"
date: "10/27/2021"
header-includes:
  - \usepackage{placeins}
output: pdf_document
bibliography: references.bib
---

@@

This document shows the simulation results for each individual site analysed in the study with some additional notes pertaining to edits to the DTM, treatment of ^14^C-dates and other relevant information. The sites are presented in alphabetical order. All underlying and derived data are available in the online repository for the paper at https://osf.io/7F9SU

@@

```{r sample_size,  echo = FALSE, out.width = "500px"}
include_graphics(here("analysis/figures/sample_size.png"))

Below follows the presentation of the individual sites. The first plot on the first row for each site shows all calibrated radiocarbon dates from the Stone Age associated with the site (see analysis/data/raw_data/radiocarbon.csv for all dates, including those falling outside of the period). The fill colour of the radiocarbon dates indicates whether they are interpreted as belonging to the same phase, and each sum indicates that multiple dates for a phase have been modelled using the Boundary function and then summed using OxCal. Each phase is assumed to be independent of other phases. A red outline indicates that the date(s) were not seen as related to the artefact inventory in the original report. The second plot on the first row displays the site location in the present day landscape on the edited DTM (i.e. highways and railways impacting the adjusted sea-level have been removed, and elevation values are interpolated from the surroundings; see main text and analysis/script/03script.R). The third plot on the first row shows the site location within the study area relative to the isobases of the shoreline displacement curves in use.

@@

```{r adalvestre1,  echo = FALSE, out.width = "500px", regfloat=TRUE}

@@

```{r dalvestre2,  echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/adalvestre2.png"))

@@

```{r alveberget8,  echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/alveberget8.png"))

@@

```{r anvik,  echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/anvik.png"))

@@

```{r auve,  echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/auve.png"))

@@

```{r bakke, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/bakke.png"))

@@

```{r brunstad24, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/brunstad24.png"))

@@

```{r brunstad25, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/brunstad25.png"))

@@

```{r dordal, echo = FALSE, out.width = "500px", regfloat=TRUE}

@@

```{r dybdalshei1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/dybdalshei1.png"))

@@

```{r dybdalshei2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/dybdalshei2.png"))

@@

```{r gunnarsrod4, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/gunnarsrod4.png"))

@@

```{r gunnarsrod5, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/gunnarsrod5.png"))

@@

```{r gunnarsrod6a, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/gunnarsrod6a.png"))

@@

```{r gunnarsrod6b, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/gunnarsrod6b.png"))

@@

```{r gunnarsrod7, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/gunnarsrod7.png"))

@@

```{r gunnarsrod10, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/gunnarsrod10.png"))

@@

```{r hegnavest1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hegnavest1.png"))

@@

```{r hegnavest2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hegnavest2.png"))

@@

```{r hegnavest3, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hegnavest3.png"))

@@

```{r hesthagc2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hesthagc2.png"))

@@

```{r hesthagc4, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hesthagc4.png"))

@@

```{r hovland1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hovland1.png"))

@@

```{r hovland3, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hovland3.png"))

@@

```{r hovland4, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hovland4.png"))

@@

```{r hovland5, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hovland5.png"))

@@

```{r hydal4, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/hydal4.png"))

@@

```{r krogenesd1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/krogenesd1.png"))

@@

```{r krogenesd2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/krogenesd2.png"))

@@

```{r kvastada1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/kvastada1.png"))

@@

```{r kvastada2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/kvastada2.png"))

@@

```{r kvastada4, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/kvastada4.png"))

@@

```{r kvastada9, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/kvastada9.png"))

@@

```{r langangenv1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/langangenv1.png"))

@@

```{r langangenv3, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/langangenv3.png"))

@@

```{r langangenv5, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/langangenv5.png"))

@@

```{r langangenv6, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/langangenv6.png"))

@@

```{r langangenv7, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/langangenv7.png"))

@@

```{r langemyr, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/langemyr.png"))

@@

```{r lovas1, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/lovas1.png"))

@@

```{r lovas2, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/lovas2.png"))

@@

```{r lovas3, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/lovas3.png"))

@@

```{r lunaveien, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/lunaveien.png"))

@@

```{r nauena, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/nauena.png"))

@@

```{r nauenc, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/nauenc.png"))

@@

```{r nordby1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/nordby1.png"))

@@

```{r nordby52, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/nordby52.png"))

@@

```{r pauler1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/pauler1.png"))

@@

```{r pauler2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/pauler2.png"))

@@

```{r pjonkerodr1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/pjonkerodr1.png"))

@@

```{r prestemoen1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/prestemoen1.png"))

@@

```{r ragnhildrod, echo = FALSE, out.width = "500px", regfloat=TRUE, warning = FALSE}
include_graphics(here("analysis/figures/ragnhildrod.png"))

@@

```{r rodbol54, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/rodbol54.png"))

@@

```{r rognlien, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/rognlien.png"))

@@

```{r sageneb1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/sageneb1.png"))

@@

```{r sageneb2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/sageneb2.png"))

@@

```{r solum3, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/solum3.png"))

@@

```{r stokkep1, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/stokkep1.png"))

@@

```{r stokkep5, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/stokkep5.png"))

@@

```{r stokkep8, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/stokkep8.png"))

@@

```{r torstvet, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/torstvet.png"))

@@

```{r trondalen, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/trondalen.png"))

@@

```{r tverdal, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/tverdal.png"))

@@

```{r vallermyrene1a, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/vallermyrene1a.png"))

@@

```{r vallermyrene1b, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/vallermyrene1b.png"))

@@

```{r vallermyrene2, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/vallermyrene2.png"))

@@

```{r vallermyrene4a, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/vallermyrene4a.png"))

@@

```{r vallermyrene4b, echo = FALSE, out.width = "500px", regfloat=TRUE}
include_graphics(here("analysis/figures/vallermyrene4b.png"))

@@

>>>>

---
title: "Supplementary material"
author: "Isak Roalkvam"
date: "10/27/2021"
header-includes:
  - \usepackage{placeins}
output: 
  pdf_document:
    toc: true
bibliography: references.bib
---

@@

## Introduction

This document presents the sensitivity analysis performed for informing the number of simulation runs in the analysis of each site, the analysis of each individual site, and the results of re-dating previously shoreline dated sites. All underlying and derived data are available in the online repository for the paper at https://osf.io/7F9SU

## Sensitivity analysis

```{r sample_size,  echo = FALSE, out.width = "500px", warning=FALSE}
include_graphics(here("analysis/figures/sample_size.png"))

## Site analysis

The presentation of simulation results for each individual site also has some additional notes pertaining to edits to the DTM, treatment of ^14^C-dates and other relevant information. The sites are presented in alphabetical order.

@@

The first plot on the first row for each site shows all calibrated radiocarbon dates from the Stone Age associated with the site (see analysis/data/raw_data/radiocarbon.csv for all dates, including those falling outside of the period). The fill colour of the radiocarbon dates indicates whether they are interpreted as belonging to the same phase, and each sum indicates that multiple dates for a phase have been modelled using the Boundary function and then summed using OxCal. Each phase is assumed to be independent of other phases. A red outline indicates that the date(s) were not seen as related to the artefact inventory in the original report. The second plot on the first row displays the site location in the present day landscape on the edited DTM (i.e. highways and railways impacting the adjusted sea-level have been removed, and elevation values are interpolated from the surroundings; see main text and analysis/script/03script.R). The third plot on the first row shows the site location within the study area relative to the isobases of the shoreline displacement curves in use.

@@

```{r adalvestre1,  echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}

@@

```{r dalvestre2,  echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
knitr::include_graphics(here("analysis/figures/adalvestre2.png"))

@@

```{r alveberget8,  echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/alveberget8.png"))

@@

```{r anvik,  echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/anvik.png"))

@@

```{r auve,  echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/auve.png"))

@@

```{r bakke, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
knitr::include_graphics(here("analysis/figures/bakke.png"))

@@

```{r brunstad24, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
knitr::include_graphics(here("analysis/figures/brunstad24.png"))

@@

```{r brunstad25, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
knitr::include_graphics(here("analysis/figures/brunstad25.png"))

@@

```{r dordal, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}

@@

```{r dybdalshei1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/dybdalshei1.png"))

@@

```{r dybdalshei2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/dybdalshei2.png"))

@@

```{r gunnarsrod4, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/gunnarsrod4.png"))

@@

```{r gunnarsrod5, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/gunnarsrod5.png"))

@@

```{r gunnarsrod6a, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/gunnarsrod6a.png"))

@@

```{r gunnarsrod6b, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/gunnarsrod6b.png"))

@@

```{r gunnarsrod7, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/gunnarsrod7.png"))

@@

```{r gunnarsrod10, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/gunnarsrod10.png"))

@@

```{r hegnavest1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hegnavest1.png"))

@@

```{r hegnavest2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hegnavest2.png"))

@@

```{r hegnavest3, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hegnavest3.png"))

@@

```{r hesthagc2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hesthagc2.png"))

@@

```{r hesthagc4, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hesthagc4.png"))

@@

```{r hovland1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hovland1.png"))

@@

```{r hovland3, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hovland3.png"))

@@

```{r hovland4, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hovland4.png"))

@@

```{r hovland5, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hovland5.png"))

@@

```{r hydal4, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/hydal4.png"))

@@

```{r krogenesd1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/krogenesd1.png"))

@@

```{r krogenesd2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/krogenesd2.png"))

@@

```{r kvastada1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/kvastada1.png"))

@@

```{r kvastada2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/kvastada2.png"))

@@

```{r kvastada4, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/kvastada4.png"))

@@

```{r kvastada9, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/kvastada9.png"))

@@

```{r langangenv1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/langangenv1.png"))

@@

```{r langangenv3, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/langangenv3.png"))

@@

```{r langangenv5, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/langangenv5.png"))

@@

```{r langangenv6, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/langangenv6.png"))

@@

```{r langangenv7, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/langangenv7.png"))

@@

```{r langemyr, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/langemyr.png"))

@@

```{r lovas1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
knitr::include_graphics(here("analysis/figures/lovas1.png"))

@@

```{r lovas2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
knitr::include_graphics(here("analysis/figures/lovas2.png"))

@@

```{r lovas3, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
knitr::include_graphics(here("analysis/figures/lovas3.png"))

@@

```{r lunaveien, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/lunaveien.png"))

@@

```{r nauena, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/nauena.png"))

@@

```{r nauenc, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/nauenc.png"))

@@

```{r nordby1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/nordby1.png"))

@@

```{r nordby52, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/nordby52.png"))

@@

```{r pauler1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/pauler1.png"))

@@

```{r pauler2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/pauler2.png"))

@@

```{r pjonkerodr1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/pjonkerodr1.png"))

@@

```{r prestemoen1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/prestemoen1.png"))

@@

```{r ragnhildrod, echo = FALSE, out.width = "500px", regfloat=TRUE, warning = FALSE, warning=FALSE}
include_graphics(here("analysis/figures/ragnhildrod.png"))

@@

```{r rodbol54, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/rodbol54.png"))

@@

```{r rognlien, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/rognlien.png"))

@@

```{r sageneb1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/sageneb1.png"))

@@

```{r sageneb2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/sageneb2.png"))

@@

```{r solum3, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/solum3.png"))

@@

```{r stokkep1, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/stokkep1.png"))

@@

```{r stokkep5, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/stokkep5.png"))

@@

```{r stokkep8, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/stokkep8.png"))

@@

```{r torstvet, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/torstvet.png"))

@@

```{r trondalen, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/trondalen.png"))

@@

```{r tverdal, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/tverdal.png"))

@@

```{r vallermyrene1a, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/vallermyrene1a.png"))

@@

```{r vallermyrene1b, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/vallermyrene1b.png"))

@@

```{r vallermyrene2, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/vallermyrene2.png"))

@@

```{r vallermyrene4a, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/vallermyrene4a.png"))

@@

```{r vallermyrene4b, echo = FALSE, out.width = "500px", regfloat=TRUE, warning=FALSE}
include_graphics(here("analysis/figures/vallermyrene4b.png"))

@@

## Numerical result of re-dating
